Effects of pulsed hollow electron lens operation on the beam core in HL-LHC: \\First experimental studies and simulations.

### 2017-07-14 resex.tex
add structure for simulation and experimental results

As there is currently no HEL installed in the LHC, the kick on the proton beam core in pulsed operation can experimentally only be approximated to first order by applying a dipole kick with the corresponding excitation pattern using the LHC transverse damper (see Section~\ref{sec:adt}). As derived in Sec.~\ref{core:sec:1}--\ref{core:sec:2} based on the measurements of the newest electron gun prototype \cite{} and in more detail in \cite{md_sim_hel_res_ex_fitterer} for the first electron gun prototype \cite{}, the expected kick to first order is for the HEL bends~(Eqn.~\ref{eqn:kick_bends}):
\begin{equation}
	\Delta x'_{\rm{bends}},\Delta y'_{\rm{bends}}\leq \SI{0.5}{nrad},
\end{equation}
and for the central region due to profile imperfections~(Eqn.~\ref{}):
\begin{equation}
	\Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} \leq \SI{15.0}{nrad}
\end{equation}
where the current HEL design parameters (see Table~\ref{tab:hllhc_param}--\ref{tab:hel_param}) were assumed yielding the maximum kick, explicitly $B_{m}=\SI{5}{T}$, $I_e=\q{5.0}{A}$, $E_{e} = \SI{10.0}{keV}$, $L=\SI{3}{m}$ and $E_{p} = \SI{7.0}{TeV}$. The contribution from the central region is clearly dominating.

@@

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}
For a perfectly uniform, annular and radially symmetric profile, the field in the region of the proton beam core vanishes (see Eqn.~\ref{eq:field_2}). In case of electron beam profile imperfections the radial symmetry is broken, leading to a residual field at the beam core. Fig.~\ref{core:fig:1} shows an example of the electric field calculated from a measured asymmetric profile.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{e-beam_profile.png}
	\caption{Calculated hollow electron beam field from measured profile of 9~kV, 2.49~A e-gun and different main solenoidal fields $Bm$. The field has been calculated using the code WARP \cite{warp}. \textcolor{red}{change $Bm$ to $B_m$ +substitute with new picture.}}
	\label{core:fig:1}
\end{figure}
A first estimate of the residual kick for the HEL design parameters (Table~\ref{tab:hel_param}--\ref{tab:hllhc_param}) with a main solenoid field of $B_{m}=\SI{5}{T}$, $I_e=\SI{5.0}{A}$, $E_{e} = \SI{10.0}{keV}$, $L=\SI{3}{m}$ and $E_{p} = \SI{7.0}{TeV}$ can be obtained by scaling the electric field at the center as obtained in Fig.~\ref{core:fig:1} with the main solenoid field $B_{m}$ and the electron beam current $I_e$ and energy $E_{e}$, yielding:
\begin{equation}
\Delta x', \Delta y'=\q{15}{nrad}
\end{equation}
\textcolor{red}{New gun measurements, can we maybe have a WARP simulation for the new design parameters instead of scaling?}

@@

\section{\label{sec:exp}LHC experiment}

>>>>

As there is currently no HEL installed in the LHC, the kick on the proton beam core in pulsed operation can experimentally only be approximated to first order by applying a dipole kick with the corresponding excitation pattern using the LHC transverse damper (see Section~\ref{sec:adt}). As derived in Sec.~\ref{core:sec:1}--\ref{core:sec:2} based on the measurements of the newest electron gun prototype \cite{} and in more detail in \cite{md_sim_hel_res_ex_fitterer} for the first electron gun prototype \cite{}, the expected kick to first order is for the HEL bends~(Eqn.~\ref{eqn:kick_bends}):
\begin{equation}
	\Delta x'_{\rm{bends}},\Delta y'_{\rm{bends}}\leq \SI{0.5}{nrad},
\end{equation}
and for the central region due to profile imperfections~(Eqn.~\ref{eqn:kick_central}):
\begin{equation}
	\Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} \leq \SI{15.0}{nrad}
\end{equation}
where the current HEL design parameters (see Table~\ref{tab:hllhc_param}--\ref{tab:hel_param}) were assumed yielding the maximum kick, explicitly $B_{m}=\SI{5}{T}$, $I_e=\q{5.0}{A}$, $E_{e} = \SI{10.0}{keV}$, $L=\SI{3}{m}$ and $E_{p} = \SI{7.0}{TeV}$. The contribution from the central region is clearly dominating.

@@

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}
For a perfectly uniform, annular and radially symmetric profile, the field in the region of the proton beam core vanishes (see Eqn.~\ref{eq:field_2}). In case of electron beam profile imperfections the radial symmetry is broken, leading to a residual field at the beam core. Fig.~\ref{core:fig:1} shows an example of the electric field calculated from a measured asymmetric profile.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{e-beam_profile.png}
	\caption{Calculated hollow electron beam field from measured profile of 9~kV, 2.49~A e-gun and different main solenoidal fields $Bm$. The field has been calculated using the code WARP \cite{warp}. \textcolor{red}{change $Bm$ to $B_m$ +substitute with new picture.}}
	\label{core:fig:1}
\end{figure}
A first estimate of the residual kick for the HEL design parameters (Table~\ref{tab:hel_param}--\ref{tab:hllhc_param}) with a main solenoid field of $B_{m}=\SI{5}{T}$, $I_e=\SI{5.0}{A}$, $E_{e} = \SI{10.0}{keV}$, $L=\SI{3}{m}$ and $E_{p} = \SI{7.0}{TeV}$ can be obtained by scaling the electric field at the center as obtained in Fig.~\ref{core:fig:1} with the main solenoid field $B_{m}$ and the electron beam current $I_e$ and energy $E_{e}$, yielding:
\begin{equation}\label{eqn:kick_central}
\Delta x', \Delta y'=\q{15}{nrad}
\end{equation}
\textcolor{red}{New gun measurements, can we maybe have a WARP simulation for the new design parameters instead of scaling?}

@@

\section{\label{sec:exp_sum}Overview of LHC experiment}

\section{\label{sec:sim}Summary of simulation results}

\section{\label{sec:exp}Summary of experimental results}

\section{\label{sec:exp_sim}Comparison of simulation and experimental results}
